The Minimal Retroreflective Microfacet Model

### 2025-12-19 article.tex
change missing notation to h and use words instead of =

\paragraph*{Shadowing-Masking.}
The shadowing-masking function combines the visibility masking function $G_1(\vecv, \vecl)$ for view direction and
$G_1(\vecl, \vecv)$ for light direction:
\begin{equation}
G_{2}(\vecv, \vecl) = G_{2}\left(G_1(\vecv, \vech), G_1(\vecl, \vech) \right) \ .
\end{equation}
Mathematically, the BSDF is plausible if $G_{2}$ is symmetric w.r.t. to exchanging $\vecv$ and $\vecl$, fulfills
$G_{2}(\vecv, \vech) \leq G_1(\vecv, \vecl)$, and if $G_1$ further establishes the correct projected area of visible micro-surfaces \cite{HeitzMicrofacet}
\begin{equation}\label{eq:visible}
  \avdot{\vecv}{\vecn} = \int_{\lbrace\vech \in \Omega_{\vecv}: \vdot{\vecv}{\vech} \geq 0\rbrace} D(\vech) \,G_1(\vecv, \vech) \vdot{\vecv}{\vech} d\vech.
\end{equation}
Choices for $G_1$ with this property are the Smith masking function
\begin{equation}
  G_1(\vecv, \vech) = G_{1,\text{Smith}}(\vecv) = \frac{\avdot{\vecv}{\vecn}}{\int_{\lbrace\vech \in \Omega_{\vecv}: \vdot{\vecv}{\vech} \geq 0\rbrace} D(\vech) \vdot{\vecv}{\vech} d\vech},
\end{equation}
where analytic expressions are available for Beckmann and GGX distributions, and the V-cavity masking function
\begin{equation}
  G_1(\vecv, \vech) = G_{1,\text{vc}, \vech}(\vdot{\vecv}{\vecn},\vdot{\vecn}{\vech},\vdot{\vecv}{\vech}) =
  \min\left\lbrace\frac{2\avdot{\vecv}{\vecn}\avdot{\vecn}{\vech}}{\avdot{\vecv}{\vech}}, 1\right\rbrace,
\end{equation}
which is generally applicable for distributions with symmetry around the normal.

@@

Getting back to the geometry term, we first note that we can rewrite $G_1(\vecv, \vech)$ as $G_1(\vecv, \vech(\vecv, \vecl))$. For ease, we write $G_1(\vecv, \vecl) = G_1(\vecv, \vech)$, and $G_1(\vecl, \vecv) = G_1(\vecl, \vech)$. It follows that using Equations \eqref{eq:khr} and \eqref{eq:kht} along with Equations \eqref{eq:nh} and \eqref{eq:nk} und using $\vech(\vecx,\vecy) = \vech(\vecy,\vecx)$ we get

>>>>

\paragraph*{Shadowing-Masking.}
The shadowing-masking function combines the visibility masking function $G_1(\vecv, \vech)$ for view direction and
$G_1(\vecl, \vech)$ for light direction:
\begin{equation}
G_{2}(\vecv, \vecl) = G_{2}\left(G_1(\vecv, \vech), G_1(\vecl, \vech) \right) \ .
\end{equation}
Mathematically, the BSDF is plausible if $G_{2}$ is symmetric w.r.t. to exchanging $\vecv$ and $\vecl$, fulfills
$G_{2}(\vecv, \vech) \leq G_1(\vecv, \vecl)$, and if $G_1$ further establishes the correct projected area of visible micro-surfaces \cite{HeitzMicrofacet}
\begin{equation}\label{eq:visible}
  \avdot{\vecv}{\vecn} = \int_{\lbrace\vech \in \Omega_{\vecv}: \vdot{\vecv}{\vech} \geq 0\rbrace} D(\vech) \,G_1(\vecv, \vech) \vdot{\vecv}{\vech} d\vech.
\end{equation}
Choices for $G_1$ with this property are the Smith masking function
\begin{equation}
  G_1(\vecv, \vech) = G_{1,\text{Smith}}(\vecv) = \frac{\avdot{\vecv}{\vecn}}{\int_{\lbrace\vech \in \Omega_{\vecv}: \vdot{\vecv}{\vech} \geq 0\rbrace} D(\vech) \vdot{\vecv}{\vech} d\vech},
\end{equation}
where analytic expressions are available for Beckmann and GGX distributions, and the V-cavity masking function
\begin{equation}
  G_1(\vecv, \vech) = G_{1,\text{vc}, \vech}(\vdot{\vecv}{\vecn},\vdot{\vecn}{\vech},\vdot{\vecv}{\vech}) =
  \min\left\lbrace\frac{2\avdot{\vecv}{\vecn}\avdot{\vecn}{\vech}}{\avdot{\vecv}{\vech}}, 1\right\rbrace,
\end{equation}
which is generally applicable for distributions with symmetry around the normal.

@@

Getting back to the geometry term, we first note that we can rewrite $G_1(\vecv, \vech)$ as $G_1(\vecv, \vech(\vecv, \vecl))$. For ease, we change the notation to $G_1(\vecv, \vecl)$ instead of $G_1(\vecv, \vech)$, and $G_1(\vecl, \vecv)$ instead of $G_1(\vecl, \vech)$. It follows that using Equations \eqref{eq:khr} and \eqref{eq:kht} along with Equations \eqref{eq:nh} and \eqref{eq:nk} und using $\vech(\vecx,\vecy) = \vech(\vecy,\vecx)$ we get
